Paper

### 2024-11-25 analysis/appendix.qmd
Add links to Word file

  <a class="btn btn-warning btn-sm mb-1" target="_blank" href="/manuscript/output/appendix+ms.pdf">
  <i class="fa-solid fa-file-arrow-down"></i>&ensp;Manuscripty PDF <small>(download)</small>
  </a>
</p>

>>>>

  <a class="btn btn-warning btn-sm mb-1" target="_blank" href="/manuscript/output/appendix+ms.pdf">
  <i class="fa-solid fa-file-arrow-down"></i>&ensp;Manuscripty PDF <small>(download)</small>
  </a>

  <a class="btn btn-info btn-sm mb-1" target="_blank" href="/manuscript/output/appendix.docx">
  <i class="fa-solid fa-file-word"></i>&ensp;Word <small>(download)</small>
  </a>
</p>

### 2024-11-25 analysis/paper.qmd
PHEW recreate google doc version + targetsify + renvify + clean up website
Add links to Word file

```{r include=FALSE}
# Add the manuscript target as a dependency to the overall website
# targets::tar_load(c(manuscript))
```

@@

  <a class="btn btn-warning btn-sm mb-1" target="_blank" href="/manuscript/output/manuscript+ms.pdf">
  <i class="fa-solid fa-file-arrow-down"></i>&ensp;Manuscripty PDF <small>(download)</small>
  </a>
</p>

>>>>

```{r include=FALSE}
# Add the manuscript target as a dependency to the overall website
targets::tar_load(c(manuscript))
```

@@

  <a class="btn btn-warning btn-sm mb-1" target="_blank" href="/manuscript/output/manuscript+ms.pdf">
  <i class="fa-solid fa-file-arrow-down"></i>&ensp;Manuscripty PDF <small>(download)</small>
  </a>

  <a class="btn btn-info btn-sm mb-1" target="_blank" href="/manuscript/output/manuscript.docx">
  <i class="fa-solid fa-file-word"></i>&ensp;Word <small>(download)</small>
  </a>
</p>
